Title

### 2018-07-31 thesis/paper/paper.tex
More demand-driven

\subsubsection{Encoding}
One option to determine inequality would be to utilise that all entities are strings of single characters. The idea is to determine the set of characters used in all entities \(C\), set them as unequal as outlined above in section \ref{subsubsec_naive} and associate each entity with their characters.\\

@@

>>>>

\subsubsection{Encoding}\label{subsubsec_encoding}
One option to determine inequality would be to utilise that all entities are strings of single characters. The idea is to determine the set of characters used in all entities \(C\), set them as unequal as outlined above in section \ref{subsubsec_naive} and associate each entity with their characters.\\

@@

To save space and avoid redundancy the following rules will not explicitly state the inequality requirement predicate. Instead, assume that for every premise with the form \(B_1 \wedge \ldots\wedge B_m \wedge I\) where \(B_1 .. B_m\) are arbitrary atoms, \(I\) is an atom of the form \(\text{unequal}(t_1, t_2)\) with \(t_1,t_2\) terms and all of \(t_1,t_2\) that are variables appear in at least one of \(B_1 \ldots B_m\), the rule 
\begin{equation*}
\text{req\_inequality}(t_1, t_2)
 \leftarrow B_1 \wedge \ldots \wedge B_m
\end{equation*} is introduced.\\

The rules outlined in section \ref{subsubsec_encoding} are changed to utilise this new requirement.
\begin{equation*}
\text{unequal}(X, Y) \leftarrow \text{req\_inequality}(X, Y) \wedge \text{letter\_i}(X, A) \wedge \text{letter\_i}(Y, B) \wedge \text{unequal}(A, B)
\end{equation*}

\todo{could use this to restrict the character inequality too but do we gain much?}
